Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
Finished sections

When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. This, coupled with the rejection of the H\texsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding. A suggestion for a follow up study would be to determine exactly  and why one inspection process finds them over the other.

@@

The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.

>>>>

When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding. A suggestion for a follow up study would be to determine why CL and UC discover different tests.

@@

Given that H\textsubscript{Eff}, H\textsubscript{Rate} and H\textsubscript{Fault} all reject their null hypothesise, we can assume that there is a noticeable difference between the two inspection methods.
